Parameter precision in economic growth models inspired by Ecological Economics

### 2015-10-03 Articles/Article_EcolEcon_2015/Paper0/Paper0-Resampling.Rnw
Better title
Added framing to the paper

\title{Estimating statical precison for parameters of Ecological Economics-inspired production functions}

@@

\author[label1]{Randall Pruim}
\ead{rpruim@calvin.edu}

@@

@@

%++++++++++++++++++++++++++++++
\subsection{Production Functions}	% 202 words on 14-09-2015
\label{sec:models}
%++++++++++++++++++++++++++++++

>>>>

\title{Parameter precision in economic growth models inspired by Ecological Economics}

@@

\author[label1]{Randall J. Pruim}
\ead{rpruim@calvin.edu}

@@

Ideas for an Ecological Economics frame for the paper:

%
\begin{itemize}

  \item EE ideas (work of Kummel and Ayres and Warr, especially) 
        inspire us to include energy, 
        reject the CSP, and 
        quality-adjust energy.

  \item Another insight from Ayres and Warr (and Kummel before them) 
        is that output elasticities can be functions of time. 
        Linex gives this explicitly. 
        But, so does CES.
        This means moving away from Cobb-Douglas toward CES.

  \item Also, inspired by Ayres and Warr, 
        we don’t want to assume elasticity of substitution 
        of unity as CD does.
        (What does Linex give for the elasticity of substitution between factors of production?)

  \item But, questions remain from Ayres and Warr's work.

  \begin{itemize}

    \item Ayres and Warr used a non-standard production function.
          Will their insights hold true for standard production functinos like Cobb-Douglas and CES?

    \item Ayres and Warr quality-adjusted only one factor of production, energy, by employing useful work.  
          What happens when all factors of production, including capital and labor, are quality-adjusted?

    \item Ayres and Warr expended minimal effort at statistical precision of estimated parameters. 
          How robust are their findings, from a statistical point of view?

  \end{itemize}

  \item We want to explore the last point above (statistical precision of estimated parameters)
        in the context of a standard production function (CES).

  \item However, when moving away from CD and Linex toward CES, 
        we leave the world of linear fitting behind.

  \item Standard approaches assume normal distributions for model parameters. 
        In the non-linear world of CES, 
        those assumptions aren't appropriate. 
        Need a new approach in the non-CD world.

  \begin{itemize}

    \item Need advanced techniques for fitting.

    \item We use customized version of Henningsen and Henningsen for fitting.

    \item Need advanced techniques for estimating precision of estimated parameters.

    \item We use resampling to estimate precision of estimated parameters.

  \end{itemize}

\end{itemize}
%
This paper explores and justifies those choices by 
%
\begin{enumerate}

  \item comparing standard techniques and our approaches for the Cobb-Douglas production function and

  \item applying our techniques to the CES production production function.

\end{enumerate}
%

@@

%++++++++++++++++++++++++++++++
\subsection{Production Functions}
\label{sec:models}
%++++++++++++++++++++++++++++++
